Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-10 Submission.Rmd
on the fly edits

We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker & Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001). To capture an effectively exhaustive list of characteristics that apply to, theoretically, *every* possible job, we consult the  unifying framework of O\*Net.

@@

```{r interrater}
interrater <- read.csv("interrater.csv")

library(irr)

kappa <- kappam.fleiss(interrater)
```
Subsequent to providing ratings of whether or not each of the 98 O\*Net characteristics were relevant for the respondent’s work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

### Characteristics, Demands, and Resources

@@

>>>>

@@

@@

Outline:

1. Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.

2. Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.

3. *Research Question 1*: Are literature-implicated resources consistently rated as job resources?

4. *Research Question 2*: Are literature-implicated challenges consistently rated as job challenges?

5. *Research Question 3*: Are literature-implicated hiderances consistently rated as job hindrances?

### 2022-12-10 Submission.tex
on the fly edits

We evaluate agreement across perceptions of job characteristics regarding their characterization as resource, challenge, and hindrance (Bakker \& Demerouti, 2017; Bakker et al., 2003; Demerouti et al., 2001). To capture an effectively exhaustive list of characteristics that apply to, theoretically, \emph{every} possible job, we consult the unifying framework of O*Net.

@@

\hypertarget{materials-1}{%
\subsection{Materials}\label{materials-1}}

Subsequent to providing ratings of whether or not each of the 98 O*Net characteristics were relevant for the respondent's work, each respondent who agreed that an element had at least some relevance to their job was then also asked to rate that element in terms of, 1) . . . this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) . . . this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) . . . this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

\hypertarget{characteristics-demands-and-resources}{%
\subsubsection{Characteristics, Demands, and Resources}\label{characteristics-demands-and-resources}}

@@

>>>>

@@

@@

Outline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
\item
  Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
\item
  \emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\item
  \emph{Research Question 2}: Are literature-implicated challenges consistently rated as job challenges?
\item
  \emph{Research Question 3}: Are literature-implicated hiderances consistently rated as job hindrances?
\end{enumerate}
